\ieeetitle

### 2017-02-06 report/figures/real-churn/total-events-sent-real-churn.tex
Correct typos in report

\begin{tikzpicture}
\pgfplotsset{width=\linewidth, height=4.7cm}
\begin{axis}[
ymin=160000,
ymax=170000,
enlarge x limits=0.3,
ybar=0,
/pgf/bar width=3mm,
/pgfplots/area legend,
nodes near coords,
legend style={
	anchor=north west,
	at={(0.6,0.97)},
	cells={anchor=west},
	draw=none,
},
every node near coord/.append style={
	rotate=90,
	anchor=north,
	font=\tiny,
	xshift=5mm,
	yshift=1mm,
},
ymajorgrids,
xtick=data,
xlabel=Protocol,
xticklabel style={text height=1.5ex, rotate=30}, 
scaled ticks=false, tick label style={/pgf/number format/fixed},
ylabel={Events sent},
symbolic x coords={EpTO, JGroups-nocoord, JGroups-coord},
]
% 100-1sec real trace
\addplot[mark=none, pattern=north east lines, error bars/.cd,y dir=both, y explicit] coordinates {
	% Events sent
	(EpTO, 165844.2) +- (0, 210.222976860287)
	(JGroups-nocoord, 166585.8) +- (0, 824.998303028558)
	(JGroups-coord, 166183) +- (0, 1368.95507596122)
};
\end{axis}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
\pgfplotsset{width=\linewidth, height=4.7cm}
\begin{axis}[
ymin=160000,
ymax=170000,
enlarge x limits=0.3,
ybar=0,
/pgf/bar width=3mm,
/pgfplots/area legend,
nodes near coords,
legend style={
	anchor=north west,
	at={(0.6,0.97)},
	cells={anchor=west},
	draw=none,
	fill=none
},
every node near coord/.append style={
	rotate=90,
	anchor=north,
	font=\tiny,
	xshift=5mm,
	yshift=1mm,
},
ymajorgrids,
xtick=data,
xlabel=Protocol,
xticklabel style={text height=1.5ex, rotate=30}, 
scaled ticks=false, tick label style={/pgf/number format/fixed},
ylabel={Events sent},
symbolic x coords={EpTO, JGroups-nocoord, JGroups-coord},
]
% 100-1sec real trace
\addplot[mark=none, pattern=north east lines, error bars/.cd,y dir=both, y explicit] coordinates {
	% Events sent
	(EpTO, 165844.2) +- (0, 210.222976860287)
	(JGroups-nocoord, 166585.8) +- (0, 824.998303028558)
	(JGroups-coord, 166183) +- (0, 1368.95507596122)
};
\end{axis}
\end{tikzpicture}

### 2017-02-06 report/figures/synthetic-churn/global-times-churn.tex
WIP report
Correct typos in report

\begin{tikzpicture}
\begin{groupplot}[
group style={
group size=2 by 1,
vertical sep=0pt,
horizontal sep=6mm,
xlabels at=edge bottom,
ylabels at=edge left,
xticklabels at=edge bottom,
yticklabels at=edge left,
},
every axis plot/.append style={very thick},
height=5cm, width=\linewidth / 1.75,
grid=major,
grid style={dashed,gray!30},
ymax=1.05,
ymin=0,
xmin=1185,
xmax=1202.5,
xlabel={Time $\left[\si{\second}\right]$},
x tick label style={/pgf/number format/fixed},
ytick={0,0.2,0.4,0.6,0.8,1},
yticklabels={0,0.2,0.4,0.6,0.8,1},
ylabel=Percentiles,
legend columns=3,
legend cell align=left,
legend style={at={(1.1,1.3)},anchor=north, font=\small, draw=none},
cycle list name=my colors,
]
\nextgroupplot
\addplot+[const plot, mark=none] table[x=EpTO-suspend-x, y=EpTO-suspend-y, col sep=comma] {\tableglobaltime};
\addplot+[const plot, mark=none] table[x=JGroups-suspend-coord-x, y=JGroups-suspend-coord-y, col sep=comma] {\tableglobaltime};
\addplot+[const plot, mark=nonee] table[x=JGroups-suspend-nocoord-x, y=JGroups-suspend-nocoord-y, col sep=comma] {\tableglobaltime};
\legend{EpTO, JGroups-nocoord, JGroups-coord}
%
\nextgroupplot
\addplot+[const plot, mark=nonek] table[x=EpTO-add-suspend-x, y=EpTO-add-suspend-y, col sep=comma] {\tableglobaltime};
\addplot+[const plot, mark=none] table[x=JGroups-add-suspend-coord-x, y=JGroups-add-suspend-coord-y, col sep=comma] {\tableglobaltime};
\addplot+[const plot, mark=none] table[x=JGroups-add-suspend-nocoord-x, y=JGroups-add-suspend-nocoord-y, col sep=comma] {\tableglobaltime};
\end{groupplot}
%
\node[anchor=south] at (group c1r1.north) {1 kill/minute};
\node[anchor=south] at (group c2r1.north) {1 \{kill,add\}/minute};
\end{tikzpicture}

>>>>

\begin{tikzpicture}
\begin{groupplot}[
group style={
group size=2 by 1,
vertical sep=0pt,
horizontal sep=6mm,
xlabels at=edge bottom,
ylabels at=edge left,
xticklabels at=edge bottom,
yticklabels at=edge left,
},
every axis plot/.append style={very thick},
height=5cm, width=\linewidth / 1.75,
grid=major,
grid style={dashed,gray!30},
ymax=1.05,
ymin=0,
xmin=1185,
xmax=1202.5,
xlabel={Time $\left[\si{\second}\right]$},
x tick label style={/pgf/number format/fixed},
ytick={0,0.2,0.4,0.6,0.8,1},
yticklabels={0,0.2,0.4,0.6,0.8,1},
ylabel=Percentiles,
legend columns=3,
legend cell align=left,
legend style={at={(1.1,1.3)},anchor=north, font=\small, draw=none, fill=none},
cycle list name=my colors,
]
\nextgroupplot
\addplot+[const plot, mark=none] table[x=EpTO-suspend-x, y=EpTO-suspend-y, col sep=comma] {\tableglobaltime};
\addplot+[const plot, mark=none] table[x=JGroups-suspend-coord-x, y=JGroups-suspend-coord-y, col sep=comma] {\tableglobaltime};
\addplot+[const plot, mark=nonee] table[x=JGroups-suspend-nocoord-x, y=JGroups-suspend-nocoord-y, col sep=comma] {\tableglobaltime};
\legend{\epto, \jgroups-nocoord, \jgroups-coord}
%
\nextgroupplot
\addplot+[const plot, mark=nonek] table[x=EpTO-add-suspend-x, y=EpTO-add-suspend-y, col sep=comma] {\tableglobaltime};
\addplot+[const plot, mark=none] table[x=JGroups-add-suspend-coord-x, y=JGroups-add-suspend-coord-y, col sep=comma] {\tableglobaltime};
\addplot+[const plot, mark=none] table[x=JGroups-add-suspend-nocoord-x, y=JGroups-add-suspend-nocoord-y, col sep=comma] {\tableglobaltime};
\end{groupplot}
%
\node[anchor=south] at (group c1r1.north) {1 kill/minute};
\node[anchor=south] at (group c2r1.north) {1 \{kill,add\}/minute};
\end{tikzpicture}

### 2017-02-06 report/figures/synthetic-churn/local-delta-churn.tex
WIP report
Correct typos in report

\begin{tikzpicture}
\begin{groupplot}[
group style={
	group size=2 by 1,
	vertical sep=0pt,
	horizontal sep=6mm,
	xlabels at=edge bottom,
	ylabels at=edge left,
	xticklabels at=edge bottom,
	yticklabels at=edge left,
},
every axis plot/.append style={very thick},
height=5cm, width=\linewidth / 1.75,
grid=major,
grid style={dashed,gray!30},
ymax=1.05,
ymin=0,
xmax=25,
scaled x ticks = false,
x tick label style={/pgf/number format/fixed},
xlabel={Time $\left[\si{\second}\right]$},
ytick={0,0.2,0.4,0.6,0.8,1},
yticklabels={0,0.2,0.4,0.6,0.8,1},
ylabel=Percentiles,
legend columns=3,
legend cell align=left,
legend style={at={(1.1,1.3)},anchor=north, font=\small, draw=none},
cycle list name=my colors,
]
\nextgroupplot
\addplot+[const plot, mark=none] table[x=EpTO-suspend-x, y=EpTO-suspend-y, col sep=comma] {\tablelocaldeltas};
\addplot+[const plot, mark=none] table[x=JGroups-suspend-coord-x, y=JGroups-suspend-coord-y, col sep=comma] {\tablelocaldeltas};
\addplot+[const plot, mark=nonee] table[x=JGroups-suspend-nocoord-x, y=JGroups-suspend-nocoord-y, col sep=comma] {\tablelocaldeltas};
\legend{EpTO, JGroups-coord, JGroups-nocoord}
%
\nextgroupplot
\addplot+[const plot, mark=none] table[x=EpTO-add-suspend-x, y=EpTO-add-suspend-y, col sep=comma] {\tablelocaldeltas};
\addplot+[const plot, mark=none] table[x=JGroups-add-suspend-coord-x, y=JGroups-add-suspend-coord-y, col sep=comma] {\tablelocaldeltas};
\addplot+[const plot, mark=none] table[x=JGroups-add-suspend-nocoord-x, y=JGroups-add-suspend-nocoord-y, col sep=comma] {\tablelocaldeltas};
\end{groupplot}
%
\node[anchor=south] at (group c1r1.north) {1 kill/minute};
\node[anchor=south] at (group c2r1.north) {1 \{kill,add\}/minute};
\end{tikzpicture}

>>>>

\begin{tikzpicture}
\begin{groupplot}[
group style={
	group size=2 by 1,
	vertical sep=0pt,
	horizontal sep=6mm,
	xlabels at=edge bottom,
	ylabels at=edge left,
	xticklabels at=edge bottom,
	yticklabels at=edge left,
},
every axis plot/.append style={very thick},
height=5cm, width=\linewidth / 1.75,
grid=major,
grid style={dashed,gray!30},
ymax=1.05,
ymin=0,
xmax=25,
scaled x ticks = false,
x tick label style={/pgf/number format/fixed},
xlabel={Time $\left[\si{\second}\right]$},
ytick={0,0.2,0.4,0.6,0.8,1},
yticklabels={0,0.2,0.4,0.6,0.8,1},
ylabel=Percentiles,
legend columns=3,
legend cell align=left,
legend style={at={(1.1,1.3)},anchor=north, font=\small, draw=none, fill=none},
cycle list name=my colors,
]
\nextgroupplot
\addplot+[const plot, mark=none] table[x=EpTO-suspend-x, y=EpTO-suspend-y, col sep=comma] {\tablelocaldeltas};
\addplot+[const plot, mark=none] table[x=JGroups-suspend-coord-x, y=JGroups-suspend-coord-y, col sep=comma] {\tablelocaldeltas};
\addplot+[const plot, mark=nonee] table[x=JGroups-suspend-nocoord-x, y=JGroups-suspend-nocoord-y, col sep=comma] {\tablelocaldeltas};
\legend{\epto, \jgroups-coord, \jgroups-nocoord}
%
\nextgroupplot
\addplot+[const plot, mark=none] table[x=EpTO-add-suspend-x, y=EpTO-add-suspend-y, col sep=comma] {\tablelocaldeltas};
\addplot+[const plot, mark=none] table[x=JGroups-add-suspend-coord-x, y=JGroups-add-suspend-coord-y, col sep=comma] {\tablelocaldeltas};
\addplot+[const plot, mark=none] table[x=JGroups-add-suspend-nocoord-x, y=JGroups-add-suspend-nocoord-y, col sep=comma] {\tablelocaldeltas};
\end{groupplot}
%
\node[anchor=south] at (group c1r1.north) {1 kill/minute};
\node[anchor=south] at (group c2r1.north) {1 \{kill,add\}/minute};
\end{tikzpicture}

### 2017-02-06 report/figures/synthetic-churn/local-times-churn.tex
WIP report
Correct typos in report

\begin{tikzpicture}
\begin{groupplot}[
group style={
group size=2 by 1,
vertical sep=0pt,
horizontal sep=6mm,
xlabels at=edge bottom,
ylabels at=edge left,
xticklabels at=edge bottom,
yticklabels at=edge left,
},
every axis plot/.append style={very thick},
height=5cm, width=\linewidth / 1.75,
grid=major,
grid style={dashed,gray!30},
ymax=1.05,
ymin=0,
xmin=1185,
xmax=1202.5,
xlabel={Time $\left[\si{\second}\right]$},
x tick label style={/pgf/number format/fixed},
ytick={0,0.2,0.4,0.6,0.8,1},
yticklabels={0,0.2,0.4,0.6,0.8,1},
ylabel=Percentiles,
legend columns=3,
legend cell align=left,
legend style={at={(1.1,1.3)},anchor=north, font=\small, draw=none},
cycle list name=my colors,
]
\nextgroupplot
\addplot+[const plot, mark=none] table[x=EpTO-suspend-x, y=EpTO-suspend-y, col sep=comma] {\tablelocaltime};
\addplot+[const plot, mark=none] table[x=JGroups-suspend-coord-x, y=JGroups-suspend-coord-y, col sep=comma] {\tablelocaltime};
\addplot+[const plot, mark=nonee] table[x=JGroups-suspend-nocoord-x, y=JGroups-suspend-nocoord-y, col sep=comma] {\tablelocaltime};
\legend{EpTO, JGroups-nocoord, JGroups-coord}
%
\nextgroupplot
\addplot+[const plot, mark=nonek] table[x=EpTO-add-suspend-x, y=EpTO-add-suspend-y, col sep=comma] {\tablelocaltime};
\addplot+[const plot, mark=none] table[x=JGroups-add-suspend-coord-x, y=JGroups-add-suspend-coord-y, col sep=comma] {\tablelocaltime};
\addplot+[const plot, mark=none] table[x=JGroups-add-suspend-nocoord-x, y=JGroups-add-suspend-nocoord-y, col sep=comma] {\tablelocaltime};
\end{groupplot}
%
\node[anchor=south] at (group c1r1.north) {1 kill/minute};
\node[anchor=south] at (group c2r1.north) {1 \{kill,add\}/minute};
\end{tikzpicture}

>>>>

\begin{tikzpicture}
\begin{groupplot}[
group style={
group size=2 by 1,
vertical sep=0pt,
horizontal sep=6mm,
xlabels at=edge bottom,
ylabels at=edge left,
xticklabels at=edge bottom,
yticklabels at=edge left,
},
every axis plot/.append style={very thick},
height=5cm, width=\linewidth / 1.75,
grid=major,
grid style={dashed,gray!30},
ymax=1.05,
ymin=0,
xmin=1185,
xmax=1202.5,
xlabel={Time $\left[\si{\second}\right]$},
x tick label style={/pgf/number format/fixed},
ytick={0,0.2,0.4,0.6,0.8,1},
yticklabels={0,0.2,0.4,0.6,0.8,1},
ylabel=Percentiles,
legend columns=3,
legend cell align=left,
legend style={at={(1.1,1.3)},anchor=north, font=\small, draw=none, fill=none},
cycle list name=my colors,
]
\nextgroupplot
\addplot+[const plot, mark=none] table[x=EpTO-suspend-x, y=EpTO-suspend-y, col sep=comma] {\tablelocaltime};
\addplot+[const plot, mark=none] table[x=JGroups-suspend-coord-x, y=JGroups-suspend-coord-y, col sep=comma] {\tablelocaltime};
\addplot+[const plot, mark=nonee] table[x=JGroups-suspend-nocoord-x, y=JGroups-suspend-nocoord-y, col sep=comma] {\tablelocaltime};
\legend{\epto, \jgroups-nocoord, \jgroups-coord}
%
\nextgroupplot
\addplot+[const plot, mark=nonek] table[x=EpTO-add-suspend-x, y=EpTO-add-suspend-y, col sep=comma] {\tablelocaltime};
\addplot+[const plot, mark=none] table[x=JGroups-add-suspend-coord-x, y=JGroups-add-suspend-coord-y, col sep=comma] {\tablelocaltime};
\addplot+[const plot, mark=none] table[x=JGroups-add-suspend-nocoord-x, y=JGroups-add-suspend-nocoord-y, col sep=comma] {\tablelocaltime};
\end{groupplot}
%
\node[anchor=south] at (group c1r1.north) {1 kill/minute};
\node[anchor=south] at (group c2r1.north) {1 \{kill,add\}/minute};
\end{tikzpicture}

### 2017-02-06 report/figures/synthetic-churn/total-bytes-churn.tex
Start working on report
Correct typos in report

\begin{tikzpicture}
\usetikzlibrary{plotmarks}
\pgfplotsset{width=\linewidth, height=4.7cm}
\begin{groupplot}[
group style={
	group size=2 by 1,
	vertical sep=0pt,
	horizontal sep=2mm,
	xlabels at=edge bottom,
	ylabels at=edge left,
	xticklabels at=edge bottom,
	yticklabels at=edge left,
},
ymin=0,
ymax=35,
width=\linewidth / 1.75,
enlarge x limits=0.3,
ybar=0,
/pgf/bar width=3mm,
/pgfplots/area legend,
nodes near coords,
legend style={
	anchor=north west,
	at={(0.6,0.97)},
	cells={anchor=west},
	draw=none,
},
every node near coord/.append style={
	rotate=90,
	anchor=north,
	font=\tiny,
	xshift=3mm,
	yshift=0.3mm,
},
ymajorgrids,
xtick=data,
xlabel=Protocol,
xticklabel style={text height=1.5ex, rotate=30}, 
ylabel={Total $\left[\si{\giga\byte}\right]$},
symbolic x coords={EpTO, JGroups-nocoord, JGroups-coord},
]
\nextgroupplot
% 100-1sec 1kill/min
\addplot+[mark=none, pattern=north east lines,pattern color=blue, error bars/.cd,y dir=both, y explicit] coordinates {
	% Receive
	(EpTO, 21.3437665258) +- (0, 0.302297622101786)
	(JGroups-nocoord, 1.3338886813) +- (0, 0.00853400183682598)
	(JGroups-coord, 1.3440551501) +- (0, 0.0164341768113215)
};
\addplot+[mark=none, pattern=crosshatch dots,pattern color=red, error bars/.cd,y dir=both, y explicit] coordinates {
	% Send
	(EpTO, 21.4504884001) +- (0, 0.0157182231373203)
	(JGroups-nocoord, 1.285075604) +- (0, 0.00872334968295833)
	(JGroups-coord, 1.2945710642) +- (0, 0.0158581561021704)
};
\legend{receive, send}
\nextgroupplot
% 100-1sec 1kill, 1add/min
\addplot+[mark=none, pattern=north east lines,pattern color=blue, error bars/.cd,y dir=both, y explicit] coordinates {
	% Receive
	(EpTO, 27.0797668262) +- (0, 0.300652054138594)
	(JGroups-nocoord, 1.6071496365) +- (0, 0.00972747186106245)
	(JGroups-coord, 1.6039433255) +- (0, 0.0084962148465832)
};
\addplot+[mark=none, pattern=crosshatch dots,pattern color=red, error bars/.cd,y dir=both, y explicit] coordinates {
	% Send
	(EpTO, 26.8856375946) +- (0, 0.0157182231373203)
	(JGroups-nocoord, 1.5459290852) +- (0, 0.00937891633596378)
	(JGroups-coord, 1.5426003209) +- (0, 0.00829044483237941)
};
\end{groupplot}
%
\node[anchor=south] at (group c1r1.north) {1 kill/minute};
\node[anchor=south] at (group c2r1.north) {1 kill/minute, 1 add/minute};
\end{tikzpicture}

>>>>

\begin{tikzpicture}
\usetikzlibrary{plotmarks}
\pgfplotsset{width=\linewidth, height=4.7cm}
\begin{groupplot}[
group style={
	group size=2 by 1,
	vertical sep=0pt,
	horizontal sep=2mm,
	xlabels at=edge bottom,
	ylabels at=edge left,
	xticklabels at=edge bottom,
	yticklabels at=edge left,
},
ymin=0,
ymax=35,
width=\linewidth / 1.75,
enlarge x limits=0.3,
ybar=0,
/pgf/bar width=3mm,
/pgfplots/area legend,
nodes near coords,
legend style={
	anchor=north west,
	at={(0.6,0.97)},
	cells={anchor=west},
	draw=none,
	fill=none,
},
every node near coord/.append style={
	rotate=90,
	anchor=north,
	font=\tiny,
	xshift=3mm,
	yshift=0.3mm,
},
ymajorgrids,
xtick=data,
xlabel=Protocol,
xticklabel style={text height=1.5ex, rotate=30}, 
ylabel={Total $\left[\si{\giga\byte}\right]$},
symbolic x coords={EpTO, JGroups-nocoord, JGroups-coord},
]
\nextgroupplot
% 100-1sec 1kill/min
\addplot+[mark=none, pattern=north east lines,pattern color=blue, error bars/.cd,y dir=both, y explicit] coordinates {
	% Receive
	(EpTO, 21.001445292) +- (0, 0.248116313343146)
	(JGroups-nocoord, 1.5381357651) +- (0, 0.0115143286137117)
	(JGroups-coord, 1.5510862161) +- (0, 0.0181726968637206)
};
\addplot+[mark=none, pattern=crosshatch dots,pattern color=red, error bars/.cd,y dir=both, y explicit] coordinates {
	% Send
	(EpTO, 21.216776898) +- (0, 0.255744716454951)
	(JGroups-nocoord, 1.4935079775) +- (0, 0.0119366849923253)
	(JGroups-coord, 1.5064716889) +- (0, 0.0186384151121228)
};
\legend{receive, send}
\nextgroupplot
% 100-1sec 1kill, 1add/min
\addplot+[mark=none, pattern=north east lines,pattern color=blue, error bars/.cd,y dir=both, y explicit] coordinates {
	% Receive
	(EpTO, 26.325256447) +- (0, 0.320079175714576)
	(JGroups-nocoord, 1.8338254834) +- (0, 0.0187827622384514)
	(JGroups-coord, 1.8511940589) +- (0, 0.0183913437417294)
};
\addplot+[mark=none, pattern=crosshatch dots,pattern color=red, error bars/.cd,y dir=both, y explicit] coordinates {
	% Send
	(EpTO, 26.5733934455) +- (0, 0.320312180261336)
	(JGroups-nocoord, 1.7777051021) +- (0, 0.0190481557873808)
	(JGroups-coord, 1.7959073697) +- (0, 0.0189017779847593)
};
\end{groupplot}
%
\node[anchor=south] at (group c1r1.north) {1 kill/minute};
\node[anchor=south] at (group c2r1.north) {1 kill/minute, 1 add/minute};
\end{tikzpicture}

### 2017-02-06 report/figures/synthetic-churn/total-events-sent-churn.tex
Start working on report
Correct typos in report

\begin{tikzpicture}
\pgfplotsset{width=\linewidth, height=4.7cm}
\begin{groupplot}[
group style={
	group size=2 by 1,
	vertical sep=0pt,
	horizontal sep=2mm,
	xlabels at=edge bottom,
	ylabels at=edge left,
	xticklabels at=edge bottom,
	yticklabels at=edge left,
},
ymin=53000,
ymax=65000,
width=\linewidth / 1.75,
enlarge x limits=0.3,
ybar=0,
/pgf/bar width=3mm,
/pgfplots/area legend,
nodes near coords,
legend style={
	anchor=north west,
	at={(0.6,0.97)},
	cells={anchor=west},
	draw=none,
},
every node near coord/.append style={
	rotate=90,
	anchor=north,
	font=\tiny,
	xshift=5mm,
	yshift=1mm,
},
ymajorgrids,
xtick=data,
xlabel=Protocol,
xticklabel style={text height=1.5ex, rotate=30}, 
scaled ticks=false, tick label style={/pgf/number format/fixed},
ylabel={Events sent},
symbolic x coords={EpTO, JGroups-nocoord, JGroups-coord},
]
\nextgroupplot
% 100-1sec 1kill/min
\addplot[mark=none, pattern=north east lines, error bars/.cd,y dir=both, y explicit] coordinates {
	% Receive
	(EpTO, 54169.6) +- (0, 158.689214084218)
	(JGroups-nocoord, 53981.9) +- (0, 102.155056436554)
	(JGroups-coord, 53953.4) +- (0, 180.331300050151)
};
%
\nextgroupplot
% 100-1sec 1kill, 1add/min
\addplot[mark=none, pattern=north east lines, error bars/.cd,y dir=both, y explicit] coordinates {
	% Receive
	(EpTO, 59853.9) +- (0, 228.339148344445)
	(JGroups-nocoord, 57813.8) +- (0, 128.414087146925)
	(JGroups-coord, 57873.3) +- (0, 150.893671172785)
};
\end{groupplot}
%
\node[anchor=south] at (group c1r1.north) {1 kill/minute};
\node[anchor=south] at (group c2r1.north) {1 \{kill,add\}/minute};
\end{tikzpicture}

>>>>

\begin{tikzpicture}
\pgfplotsset{width=\linewidth, height=4.7cm}
\begin{groupplot}[
group style={
	group size=2 by 1,
	vertical sep=0pt,
	horizontal sep=2mm,
	xlabels at=edge bottom,
	ylabels at=edge left,
	xticklabels at=edge bottom,
	yticklabels at=edge left,
},
ymin=53000,
ymax=65000,
width=\linewidth / 1.75,
enlarge x limits=0.3,
ybar=0,
/pgf/bar width=3mm,
/pgfplots/area legend,
nodes near coords,
legend style={
	anchor=north west,
	at={(0.6,0.97)},
	cells={anchor=west},
	draw=none,
	fill=none,
},
every node near coord/.append style={
	rotate=90,
	anchor=north,
	font=\tiny,
	xshift=5mm,
	yshift=1mm,
},
ymajorgrids,
xtick=data,
xlabel=Protocol,
xticklabel style={text height=1.5ex, rotate=30}, 
scaled ticks=false, tick label style={/pgf/number format/fixed},
ylabel={Events sent},
symbolic x coords={EpTO, JGroups-nocoord, JGroups-coord},
]
\nextgroupplot
% 100-1sec 1kill/min
\addplot[mark=none, pattern=north east lines, error bars/.cd,y dir=both, y explicit] coordinates {
	% Receive
	(EpTO, 53898.5) +- (0, 133.952935350029)
	(JGroups-nocoord, 53830.5) +- (0, 200.355933278752)
	(JGroups-coord, 53834.7) +- (0, 175.463861426411)
};
%
\nextgroupplot
% 100-1sec 1kill, 1add/min
\addplot[mark=none, pattern=north east lines, error bars/.cd,y dir=both, y explicit] coordinates {
	% Receive
	(EpTO, 59798.6) +- (0, 140.107260498678)
	(JGroups-nocoord, 59450.5) +- (0, 175.171820412607)
	(JGroups-coord, 59507.9) +- (0, 240.914669079693)
};
\end{groupplot}
%
\node[anchor=south] at (group c1r1.north) {1 kill/minute};
\node[anchor=south] at (group c2r1.north) {1 \{kill,add\}/minute};
\end{tikzpicture}

### 2017-02-06 report/framework.tex
Correct typos in report

\section{EpToTester}
\label{sec:epto}
\eptotester is a framework using Docker and Docker Swarm. It is designed to ease the deployment of large scale distributed systems, more particularly \jgroups and \epto. We use \eptotester to assess the claims made in \autocite{matos2015epto}. Although the implementation of \epto is written with benchmarking in mind, the code can be adapted for real applications with only minimal changes to the sources. We  use \eptotester instead of other solutions such as SPlay, which only supports LUA, as we need to test existing protocols written in different programming languages.
\subsection{Deployment}
\begin{figure}[htp]
	\centering
	\includegraphics[width=\linewidth]{figures/complete-architecture.pdf}
	\vspace{-2mm} 
	\caption[Caption]{\epto using the \eptotester framework\footnotemark}
	\vspace{-2mm} 
	\label{fig:complete-architecture}
\end{figure}
\footnotetext{This figure is partially inspired from a figure in \autocite{vaucher2016erasure}}
To deploy a protocol in our framework we need two different Docker Swarm services: one containing the tracker and one containing all replicas. Both of these services use the same network overlay to communicate. This is achieved using Docker and especially the new Docker Swarm introduced in Docker 1.12. This lets us have a unified way of deploying our benchmarks locally or remotely on vastly different clusters with minimal modifications. Every benchmark is started through a Python script available on the master node. This script handles everything from starting benchmarks, scaling the cluster during a churn and collecting results through the framework python classes. Application, churn and cluster  parameters are customizable through YAML configuration files. Tracker and replica communication is up to the user. For example, \epto uses HTTP, while \jgroups uses TCP directly.
Gradle\footnote{\href{https://gradle.org/}{https://gradle.org/}} is used to automate the project building. Finally, a script is provided to push the images to a repository accessible to the remote cluster and to push the benchmarking framework on the master node. \jgroups uses the same deployment method. Our framework applied to \epto can be seen in \autoref{fig:complete-architecture}.
\subsection{Fault Injection}
Our framework supports the ability to inject synthetic and real traces thanks to the work done in \autocite{vaucher2016erasure}. The synthetic churn provided by it was improved to support adding and removing nodes at the same time.

Synthetic churn follows strict periods. Every period of time, it modifies the cluster size according to the instructions, until there are no more steps. These instructions can either, do nothing, increase the cluster size, reduce the cluster size or both at the same time.

Real traces are based on FTA traces as stated earlier. Every time we query the database, we obtain every cluster change that happened since the last query according to the trace. Thus the smaller the period, the more accurate it is regarding to the real trace.
\subsection{Extensions}
\eptotester is a general framework and should satisfy most decentralized applications needs with almost no tweaking. However, some protocols are centralized. This is the case for \jgroups. \jgroups relies on MULTICAST and has a coordinator that order every events sent. \eptotester is written such that the main Benchmark and Churn modules are extensible to suit any need. In our experiments we wrote an extension of the Churn module, so that it can deal with the coordinator, killing it only when we want to. This provides us with fine-grained control over the benchmarks.

>>>>

\section{EpToTester}
\label{sec:epto}
\eptotester is a framework using Docker and Docker Swarm. It is designed to ease the deployment of large scale distributed systems, more particularly \jgroups and \epto. We use \eptotester to assess the claims made in \autocite{matos2015epto}. Although the implementation of \epto is written with benchmarking in mind, the code can be adapted for real applications with only minimal changes to the sources. We  use \eptotester instead of other solutions such as SPlay, which only supports LUA, as we need to test existing protocols written in different programming languages.
\subsection{Deployment}
\begin{figure}[htp]
	\centering
	\includegraphics[width=\linewidth]{figures/complete-architecture.pdf}
	\vspace{-2mm} 
	\caption[Caption]{\epto using the \eptotester framework\footnotemark}
	\vspace{-2mm} 
	\label{fig:complete-architecture}
\end{figure}
\footnotetext{This figure is partially inspired from a figure in \autocite{vaucher2016erasure}}
To deploy a protocol in our framework we need two different Docker Swarm services: one containing the tracker and one containing all replicas. Both of these services use the same network overlay to communicate. This is achieved using Docker and especially the new Docker Swarm introduced in Docker 1.12. This lets us have a unified way of deploying our benchmarks locally or remotely on vastly different clusters with minimal modifications. Every benchmark is started through a Python script available on the master node. This script handles everything from starting benchmarks, scaling the cluster during a churn and collecting results through the framework Python classes. Application, churn and cluster  parameters are customizable through YAML configuration files. Tracker and replica communication is up to the user. For example, \epto uses HTTP, while \jgroups uses TCP directly. Tracker implementation is also left to the user, although a REST Tracker implemented in Python is provided by default. The user can also opt to not use a tracker at all.
Gradle\footnote{\href{https://gradle.org/}{https://gradle.org/}} is used to automate the project building. Finally, a script is provided to push the images to a repository accessible to the remote cluster and to push the benchmarking framework on the master node. \jgroups uses the same deployment method. Our framework applied to \epto can be seen in \autoref{fig:complete-architecture}.
\subsection{Fault Injection}
Our framework supports the ability to inject synthetic and real traces thanks to the work done in \autocite{vaucher2016erasure}. The synthetic churn provided by it was improved to support adding and removing nodes at the same time.

Synthetic churn follows strict periods. Every period of time, it modifies the cluster size according to the instructions until there are no more steps. These instructions can either: do nothing, increase the cluster size, reduce the cluster size or both at the same time.

Real traces are based on FTA traces as stated earlier. Every time we query the database, we obtain every cluster change that happened since the last query according to the trace and the time elapsed between both queries. Thus, the smaller the period, the more accurate it is regarding to the real trace.
\subsection{Extensions}
\eptotester is a general framework and should satisfy most decentralized applications needs with almost no tweaking. However, some protocols are centralized. This is the case for \jgroups. \jgroups relies on MULTICAST and has a coordinator that order every events sent. \eptotester is written such that the main Benchmark and Churn modules are extensible to suit any need, thanks to class inheritance. In our experiments we wrote an extension of the Churn module, so that it can deal with the coordinator, killing it only when we want to. This provides us with fine-grained control over the benchmarks.

### 2017-02-06 report/future-work.tex
Correct typos in report

\section{Future Work}
\label{sec:future-work}
\jt{Do we have Push-Pull references?}
Future work should focus on testing \epto on a bigger cluster, preferably at a point where \jgroups can no longer function, as \epto is designed to work on very large number of peers. As it is, \epto does indeed work as intended in our infrastructure and under churn, but a larger test would showcase \epto's ability to handle large peer numbers.
\par
Future work also includes working on an alternate \epto dissemination algorithm. This algorithm would use a Push-Pull approach to further reduce the needed number of balls in the system and thus reduce the network load.

>>>>

\section{Future Work}
\label{sec:future-work}
Future work should focus on testing \epto on a bigger cluster, preferably at a point where \jgroups can no longer function, as \epto is designed to work on very large number of peers. As it is, \epto does indeed work as intended in our infrastructure and under churn, but a larger test would showcase \epto's ability to handle large peer numbers. Some preliminary tests were done on AWS EC2\footnote{https://aws.amazon.com/}. Unfortunately we encountered a Docker bug that would not let us run our benchmarks. Some preliminary work have been done on the framework to use Kubernetes\footnote{https://kubernetes.io/} with some success.
\par
Future work also includes working on an alternate \epto dissemination algorithm. This algorithm would use a Push-Pull approach to further reduce the needed number of balls in the system and thus reduce the network load. An early prototype has been designed and implemented, but not yet tested.
